---
title: "idk"
author: "Sophia Zhu"
description: |
  If you clicked on this link, guess my project was a success!
output:
  html_document:
    df_print: paged
site: distill::distill_website
---
## Introduction
Alas, what have you stumbled into? 

# Goals 
Discover how to make the optimal fake news title, or basically, what makes a fake news article good?

Checklist:
1. What words do they use? What topics do they talk about? 
2. What about the length of the sentence? 

### Details 
How can I analyze fake news titles? 
Just because I think that the wording of a headline is crucial, is that actually true? 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) 
library(tidyverse)
library(tidyr)
library(dplyr)
library(rmarkdown)
```

## Breaking down the Data
# Investigation 1 - The Almighty Words of Fake News Headlines

### [Data](https://github.com/BuzzFeedNews/2018-12-fake-news-top-50)
Here is a short sample of data if you want to scroll through, sorted by the amount of Facebook likes they garnered. 

```{r, table}
titledata <- read.csv("newstitle1.csv")
paged_table(titledata)
```

### First Investigation: Most popular words
 
<div>
After going through ~7900 headlines, these are the most popular words! It's extremely fascinating, I know. 
</div>

```{r, first graph}
titledata %>%
  select(title, category) %>%
  slice(1:7900) %>% 
  mutate(title = strsplit(as.character(title), " ")) %>% 
  unnest(title) %>% 
  group_by(title) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  slice(1:10) %>% 

ggplot(mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines", 
     subtitle = "Wow! What a diverse range of words, could totally make a headline out of it!", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```

Hmm... Something about this graph doesn't seem right. Let's clean this data up by removing duplicates, punctuation, and prepositions! That'd give us a better idea of what people enjoy to read about, and allow us to find the best subject to center our article around!

```{r}
titledata <- read.csv("newstitle1.csv")
removedata <- titledata %>%
  select(title, category) %>%
  slice(1:7900) %>%
  mutate(title = strsplit(as.character(title), " ")) %>%
  unnest(title) %>%
  group_by(title) %>%
  summarize(total = n()) %>%
  arrange(desc(total)) %>%
  slice(1:50)

newdata <- removedata[c(4, 15, 16, 17, 21, 25, 28, 29, 30, 37),]
ggplot(newdata, mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines (Edited)",
     subtitle = "Painfully obvious what year this is from", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```
 
